### 2020-08-24 ART_Czarnik/Czarnik-PU.tex
A. Figarski correctons added. Sending to the authors

\begin{artengenv}{Szymon Czarnik}
	{How much truth is in stereotypes?}
	{How much truth is in stereotypes?}
	{How much truth is in stereotypes?}
	{Institute of Sociology, Jagiellonian Universitys}
	{Stereotype accuracy is a contentious topic. Part of the problem is that typically stereotypes are generic statements whose truth status is unclear due to the fact that they are ill-defined quantitatively. The article focuses on the epistemic aspect of stereotypical beliefs. In the ongoing debate, I side with those who argue against stereotypes being wrong or inaccurate by virtue of definition alone. I propose that, when possible, stereotype accuracy should be assessed in probabilistic terms by inspecting how likely a generic statement is to be true when applied to individual(s) representative of the relevant group(s). This approach applies equally well to investigating the actual and the perceived accuracy of stereotypes.}
	{stereotypes, stereotype accuracy, epistemology, probabilistic approach.}

@@

This is the perfect stereotype. Its hallmark is that it precedes the use of reason; is a form of perception, imposes a certain character on the data of our senses before the data reach the intelligence […]. There is nothing so obdurate to education or to criticism as the stereotype. (p. 98)
}

@@

 And then: ``We can distinguish between a valid generalization and a stereotype only if we have solid data concerning the existence of (the probability of) true group differences.'' 

@@

\parencite[][p.192]{allport_nature_1954}}

>>>>

\begin{artengenv}{Szymon Czarnik}
	{How much truth is in stereotypes?}
	{How much truth is in stereotypes?}
	{How much truth is in stereotypes?}
	{Institute of Sociology, Jagiellonian University}
	{Stereotype accuracy is a contentious topic. Part of the problem is that typically stereotypes are generic statements whose truth status is unclear due to the fact that they are ill-defined quantitatively. The article focuses on the epistemic aspect of stereotypical beliefs. In the ongoing debate, I side with those who argue against stereotypes being wrong or inaccurate by virtue of definition alone. I propose that, when possible, stereotype accuracy should be assessed in probabilistic terms by inspecting how likely a generic statement is to be true when applied to individual(s) representative of the relevant group(s). This approach applies equally well to investigating the actual and the perceived accuracy of stereotypes.}
	{stereotypes, stereotype accuracy, epistemology, probabilistic approach.}

@@

This is the perfect stereotype. Its hallmark is that it precedes the use of reason; is a form of perception, imposes a certain character on the data of our senses before the data reach the intelligence […]. There is nothing so obdurate to education or to criticism as the stereotype. (p.98)
}

@@

 And then: ``We can distinguish between a valid generalization and a stereotype only if we have solid data concerning the existence of (the probability of) true group differences'' 

@@

\parencite[][p.192]{allport_nature_1954}.}
